PANCHANGE_analysis

### 2020-08-26 PANCHANGE_analysis.Rmd
cleaning up Gender per Sample

# Ethnicity
```{r Ethnicity per Sample}
Ethnicity_by_Sample <- dat %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

Ethnicity_by_Sample
```

# Ethnicity
```{r Ethnicity per Sample}
Ethnicity_by_Sample <- dat %>%
  group_by(Sample) %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

Ethnicity_by_Sample
```

```{r Ethnicity by Sample plot}
Ethnicity_by_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    #    position = "dodge",
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6,
    #    labels = c("Prepandemic", "Retrospective")
  ) +
  coord_flip()
```

# Gender
```{r Gender per Sample prop per total}
dat %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r Gender per Sample prop per Sample}
dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r Gender per Sample prop cross table}
dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))
```

```{r Gender per Sample count cross table}
dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n)
```

```{r}
dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Gender) %>%
  chisq.test() %>%
  glance()
```

>>>>

# Ethnicity
```{r Ethnicity per Sample prop per total}
Ethnicity_by_Sample_prop_total <- dat %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

Ethnicity_by_Sample_prop_total
```

```{r Ethnicity per Sample prop per sample}
Ethnicity_by_Sample_prop_sample <- dat %>%
  group_by(Sample) %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

Ethnicity_by_Sample_prop_sample
```

```{r Ethnicity per Sample prop cross table}
dat %>%
  group_by(Sample) %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))
```

```{r Ethnicity per Sample count cross table}
dat %>%
  count(Ethnicity, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )
```

```{r Ethnicity per Sample chisquare test}
dat %>%
  count(Ethnicity, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Ethnicity) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%  
  chisq.test() %>%
  glance()
```

```{r Ethnicity by Sample plot}
Ethnicity_by_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()
```

# Gender
```{r Gender per Sample prop per total}
Gender_per_Sample_prop_total <- dat %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Gender_per_Sample_prop_total)
Gender_per_Sample_prop_total
```

```{r Gender per Sample prop per Sample}
Gender_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Gender_per_Sample_prop_Sample)
Gender_per_Sample_prop_Sample
```

```{r Gender per Sample prop cross table}
Gender_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(Gender_per_Sample_prop_Sample_cross_table)
Gender_per_Sample_prop_Sample_cross_table
```

```{r Gender per Sample count cross table}
Gender_per_Sample_count_cross_table <- dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(Gender_per_Sample_count_cross_table)
Gender_per_Sample_count_cross_table
```

```{r Gender per Sample chisquare test}
Gender_per_Sample_chissquare_test <- dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Gender) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(Gender_per_Sample_chissquare_test)
Gender_per_Sample_chissquare_test
```
